Manuscript 62524 --- Response to reviewers

### 2025-08-29 Manuscript/Ant_Cactus_RESPONSE.tex
Updates

\comment{The study "Demographic consequences of partner diversity and turnover in a multi-species ant-plant mutualism" uses a long-term dataset to look at the demography of a plant with mutualistic ants that provide defense to the plant. 
The estimated parameters and used a stochastic, multi-state IPM to look at the effects of ant mutualists on plant fitness. 
Most significantly, the authors found all ant species increased fitness (finite rate of growth), irrespective of their identity or turnover over the life of the plant. 
Overall, I found the study to be high-quality and novel, and the main finding is somewhat perplexing and would be of interest of the journal's readership. 
Admittedly, I found the framing of the introduction to not quite set up the study strongly and I was worried about the precision of the modeling, but the data and their implications are compelling and interesting. 
The level of precision of the modeling that concerned me was philosophical rather than practical. 
Specifically, I spent a few days thinking about this study with respect to Levins' (1966) strategies of model building in population biology. 
I originally thought that this population model was one that focused on *precision* and either generality or realism, but upon reflection I see this as one that sacrifices precision for generality and realism because the results and interpretation are largely focused on the qualitative outcome of the model, which are the useful and meaningful results. 
I think that it was really just the first paragraph of the introduction that was a sticking point for me given that mutualism "deterioration" and context dependency didn't seem to be important for the study.}
\response{We appreciate the reviewer's positive comments about our manuscript and their thoughtful reflection of how our work relates to broader philosophical considerations of ecological modeling. 
We agree with the Reviewer's conclusion that, in the context of Levins' triangle, our work leans toward generality and realism at the expense of precision. 
That is, we have built a general model of demographic transitions (births, deaths, growth, and partner turnover) that is realistic with respect to our study system, but we query the model for qualitative inference (e.g., asking whether a multi-partner scenario yields higher or lower fitness than the single best partner) and not quantitative precision. 
We now use stronger ``signposting'' in the presentation of the model to make this clearer for readers (e.g., lines \ref{}, \ref{}). 
%******** Tom have you already done this? Or is this something you would like me to do?
}

@@

\comment{A bit jarring out the gate. The first sentence states: everyone in mutualism benefits (full stop). The second sentence is : except when they don't.}
\response{We have revised the first sentence (line \ref{ms-res:R2_1}) to reflect that in mutualisms everyone receives a net benefit rather than just saying everyone benefits.}

>>>>

\comment{The study "Demographic consequences of partner diversity and turnover in a multi-species ant-plant mutualism" uses a long-term dataset to look at the demography of a plant with mutualistic ants that provide defense to the plant. 
The estimated parameters and used a stochastic, multi-state IPM to look at the effects of ant mutualists on plant fitness. 
Most significantly, the authors found all ant species increased fitness (finite rate of growth), irrespective of their identity or turnover over the life of the plant. 
Overall, I found the study to be high-quality and novel, and the main finding is somewhat perplexing and would be of interest of the journal's readership. 
Admittedly, I found the framing of the introduction to not quite set up the study strongly and I was worried about the precision of the modeling, but the data and their implications are compelling and interesting. 
The level of precision of the modeling that concerned me was philosophical rather than practical. 
Specifically, I spent a few days thinking about this study with respect to Levins' (1966) strategies of model building in population biology. 
I originally thought that this population model was one that focused on *precision* and either generality or realism, but upon reflection I see this as one that sacrifices precision for generality and realism because the results and interpretation are largely focused on the qualitative outcome of the model, which are the useful and meaningful results. 
I think that it was really just the first paragraph of the introduction that was a sticking point for me given that mutualism "deterioration" and context dependency didn't seem to be important for the study.}
\response{We appreciate the reviewer's positive comments about our manuscript and their thoughtful reflection of how our work relates to broader philosophical considerations of ecological modeling. 
We agree with the Reviewer's conclusion that, in the context of Levins' triangle, our work leans toward generality and realism at the expense of precision. 
That is, we have built a general model of demographic transitions (births, deaths, growth, and partner turnover) that is realistic with respect to our study system, but we query the model for qualitative inference (e.g., asking whether a multi-partner scenario yields higher or lower fitness than the single best partner) and not quantitative precision. 
We now use stronger ``signposting'' in the presentation of the model to make this clearer for readers (e.g., lines \ref{ms-res:gen1}, \ref{ms-res:model_story}). 
}

@@

\comment{A bit jarring out the gate. The first sentence states: everyone in mutualism benefits (full stop). The second sentence is : except when they don't.}
\response{We have revised the first sentence (line \ref{ms-res:L1}) to reflect that in mutualisms everyone receives a net benefit rather than just saying everyone benefits.}
